A Data-Driven Framework for Neural Field Modeling

### 2011-01-03 ltx/first_order_framework/response_to_reviews.tex

    \section{Reviewer 2}

    We thank the author for their encouraging review. Each point raised is dealt with in turn.

\begin{enumerate}
    \item The handling of the (to borrow a term from numerical weather forecasting) `sub-grid scale physics' is inadequate for nervous systems (see, e.g., equation 8 [The nonlinear IntegroDifference Equation]). I do very much appreciate the spectral estimation of spatial and temporal scales. But the model errors are lumped into an iid model error term that is not realistic. For instance, the flow of potassium in the extracellular spaces has a known dynamic that will affect network excitability, generating important sub-grid dynamics that is anything but iid. See, for instance, the example in Ullah et al PLoS Comp Biol 2010 where without such dynamics, state tracking and parameter estimation for a neural system fails. A beautiful overview of sub-grid effects in data assimilation is found in Kalnay's 2003 book. I would very much value the authors comments on these issues. I guess were I to respond to this question, that I might consider extending the model error term to an autoregressive model. But I will let the authors answer this question.\\

	\emph{To address this point, we have added an extra section to the discussion, 'Modeling Asusumptions'. Within this section we discuss model mismatch and what we think is a good way to deal with it.}

@@

\item Although we all know the 1970s version of Wilson and Cowan's field equations, there was an intriguing stochasticization of these equations by Benayoun et al PloS Comp Biol 2010. I and others will value the authors' thoughts of how a more palatable stochasticization of these field equations might influence the future development of the data-assimilation framework presented in this paper.

\emph{I think the paper that he is talking about uses the central limit theorem, approximating a large number of independent neurons as have Gaussian noise. The paper he is talk about is also a nightmare to read.}

\emph{We added the disturbance term to the firing rate function  (equation 12). Although we added this after we provided the model derivation and discritization, we can show this holds if we assume the disturbance is a Wiener process, add it to the firing rate $g(\mathbf{r},t)$ (equation 3), use Ito's method to form the IDE, and the Euler-Maruyama method for the discretization. The disturbance will then be an incremental Wiener process. We chose the simplest method to present the model so the paper did not get too heavy in the maths (at least in the intro) and due to space considerations. }

\emph{We assume the neuronal firing that is not predicted by the model to be caused by external independent influences. Since we a talking about a large number of neurons, we expect this disturbance to be Gaussian (according to the central limit theorem). Furthermore, we expect the disturbance to be spatially colored according to the covariance function $\sigma_d\gamma(\mathbf{r}-\mathbf{r}')$, since we consider small neighboring regions within the field to be functional processing units.}

### 2011-01-03 ltx/first_order_framework/LaTeX_Manuscript.tex
changed fig1 caption

\newpage
\clearpage
\section*{Figure Legends}
{\bf Figure 1. Mexican-hat connectivity kernel.} The kernel is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape. The kernel decays asymptotically to zero.

>>>>

\newpage
\clearpage
\section*{Figure Legends}
{\bf Figure 1. Mexican-hat connectivity kernel.} \parham{(comment 8, reviewer 2) The kernel is a composite of three Gaussian basis functions (dashed lines), representing short-range excitation, mid-range inhibition and long-range excitation.} The kernel is rotationally symmetric (isotropic) about zero, hence a cross-section captures the important aspect of the connectivity kernel's shape. The kernel decays asymptotically to zero.
